%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Kyle Schmidt} % Your name
\address{537 W. 49th St. \\ New York, NY 10019} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(941)$\cdot$313$\cdot$0492 \\ kyle.a.schmidt@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Columbia University} \hfill {\em February 2014} \\ 
B.A. in Applied Mathematics \\
%Minor in Linguistics \smallskip \\
Treasurer of Columbia College Student Council \\
Member of Columbia University Men's Heavyweight Rowing Team \\
Jerry and Evelyn Bishop Scholar \\
%Overall GPA: 5.678

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Kepler Group}{October 2014 - Present}{Data Engineer}{New York, NY}
\item Architect and engineer scalable SQL databases, Hadoop Distributed File Systems, and microservices that facilitate seamless data transfers, maintain data integrity, and incorporate intelligent business logic.
\item Conduct ad-hoc analytical support as well as construct internal software products for Kepler's marketing teams in order to determine campaign performance and guide optimizations.
%\item Nam tincidunt congue enim, ut porta lorem Microsoft SQL lacinia consectetur.
%\item Donec ut libero sed arcu vehicula ultricies a non tortor. Lorem ipsum dolor sit amet, consectetur adipiscing elit.
%\item Pellentesque auctor nisi id magna consequat JavaScript sagittis.
%\item Aliquam at massa ipsum. Quisque bash bibendum purus convallis nulla ultrices ultricies.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Marketing Management Analytics (MMA)}{March 2014 - October 2014}{Statistical Analyst}{New York, NY}
\item Composed marketing mix models to drive measurable improvements to clients' marketing ROI by identifying and quantifying the short and long term impact of marketing, promotion, pricing, operational, competitive and economic conditions on their business.
\item Integrated information systems and statistics to build predictive models to forecast sales and revenue using R, SAS, and Microsoft Excel.
%\item Cum sociis natoque penatibus et magnis dis MySQL parturient montes, nascetur ridiculus mus.
%\item In rutrum accumsan ultricies. Mauris vitae nisi at sem facilisis semper ac in est.
%\item Nullam cursus suscipit nisi, et ultrices justo sodales nec. Fusce venenatis facilisis lectus ac semper.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Dataminr}{September 2013 - December 2013}{Product Intern}{New York, NY}
\item Performed client analysis of user behavior as well as endorsement analysis of the voting team.
\item Documented bugs for product development.
\item Code review and project management of the ‘Agora’ platform that enables machine learning to tag and describe associated companies for breaking stock market news via Twitter Tweets.
%\item Curabitur venenatis pulvinar tellus gravida ornare. Sed et erat faucibus nunc euismod ultricies ut id
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Columbia Business School}{January 2013 - August 2013}{Research Assistant}{New York, NY}
\item Analyzed degrees of separation of lexicon between economic sectors using k-nearest neighbors, 
regression analysis, and numerical methods in the R computer language in order to associate sociological commonalities with stock performance.
\item Created weekly research updates in order to facilitate collaboration among the research team.
%\item Quisque mi metus, unit tests CSS ornare sit amet fermentum et, tincidunt et orci.
%\item Curabitur venenatis pulvinar tellus gravida ornare. Sed et erat faucibus nunc euismod ultricies ut id
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, Hive, R, MATLAB, Common Lisp \\
Protocols \& APIs & XML, JSON, REST \\
Databases & Hadoop, MySQL \\
Tools & Vim
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
